---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
```

# fluents <img src='man/figures/logo.svg' align="right" height="139" />

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/fluents)](https://CRAN.R-project.org/package=fluents)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `{fluents}` is to be an opinionated R package re-implementation of
[grind.R](https://tbb.bio.uu.nl/rdb/grindR.html) by Rob de Boer, Theoretical
Biology and Bioinformatics, University of Utrecht. `grind.R` is a port from the
same author C-based program [GRIND (GReat INtegrator Differential
equations)](https://tbb.bio.uu.nl/rdb/grindC.html) to R.

`{fluents}` aims at packing the same functionality as `grind.R`, departing from
`grind.R` in a few ways:

- `{fluents}` is an R package, `grind.R` is a script.
- `{fluents}` is under public version control at GitHub, facilitating open
collaboration and easy distribution.
- `{fluents}`'s API has more functions that do less each, while `grind.R`'s has
fewer functions that do more each.

## Installation

You can install the current version of `{fluents}` with:

``` r
# install.packages("remotes")
remotes::install_github("ramiromagno/fluents")
```

## Example

```{r lotka, dpi=300, fig.width=6, fig.height=3, out.width=600}
library(fluents)

# `m`: Lotka-Volterra model
m <- function(t, state, parms) {
  with(as.list(c(state, parms)), {
    dR <- r * R * (1 - R / K) - a * R * N
    dN <- c * a * R * N - delta * N
    
    return(list(c(dR, dN)))
  })
}

# `p`: vector of parameters
p <- c(
  r = 1,
  K = 1,
  a = 1,
  c = 1,
  delta = 0.5
)

# `s`: vector of initial state
s <- c(R = 1, N = 0.01)

# `t`: time points
t <- seq(0, 100, by= 1)

# Integrate the ODE
sol <- solve(s = s, p = p, m = m, t = t)

# Make a time plot of the solution `sol`
tidyr::pivot_longer(sol, cols = c("R", "N"), names_to = "var", values_to = "pop") %>%
ggplot(aes(x = t, y = pop, col = var)) +
  geom_line()

# Find steady states
steady_states(
  s0 = tidyr::expand_grid(R = seq(0, 1, 0.1), N = seq(0, 1, 0.1)),
  p = p,
  m = m
  )
```

## From `grind.R` to `{fluents}`

| grind.R                        | fluents                                          |
|------------------------------- |--------------------------------------------------|
| `run()`                        | `solve()`                                        | 
| `newton()`                     | `steady_states()`                                |

